Output Summary

### 2021-10-15 03-post-process/output-plots.Rmd

# Carcass Correction
L1 = "Carcass Correction Factor"
L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
z_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

>>>>

# Carcass Correction
L1 = "Carcass Correction Factor"
z_diags = diag_fn("z", L1 = L1)
